Progress report

### 2018-05-28 Report/progress-report.Rmd

```{r, echo = F,warning=FALSE}
ggplot(walk_all, aes(x = condition, y = errors, fill=factor(exp_block_id))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95),geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")

>>>>

```{r, echo = F,warning=FALSE}
ggplot(walk_all, aes(x = condition, y = errors, fill=factor(exp_block_id))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95),geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar")
```
